Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-29 Articles/Article 1/main.tex
.
added interpolation equations

@@

Firstly, from the coordinates of our POI, we calculate the coordinates of the eight surrounding cells in the obstacle grid, by rounding the coordinates up and down in x, y, and z directions.

@@

Subsequently, we separately perform trilinear interpolation for each direction of the repulsive velocity vector. It is important to consider that the calculated repulsive velocity values are located at the centers of the cells. Therefore, during interpolation, we shift the values of the cells coordinates by half the resolution of the obstacle grid for each direction. This results in a repulsive velocity vector that transitions smoothly between the discrete values calculated at distinct points in the obstacle grid.

>>>>

\alert{Maybe add a sentence about computer effeciency of the method, as it is not dependent on the number of obstacles.}

@@

Firstly we use our kernel matrix multiplication method, to calculate the repulsive velocity values for the eight surrounding cells that are closest to the chosen POI. We get the indexes of the surrounding cells by first scaling the POI position by grid resolution and than rounding the position to the nearest lower and upper integer positions.

\begin{equation}
 \vec{P} = \vec{p}_{\mathrm{POI}} \times\Delta \mathrm{grid}
\end{equation}

%\begin{equation}
% X = \left[ \lfloor p_{x} \rfloor, \lceil p_{x} \rceil \right] 
%\end{equation}
%
%\begin{equation}
% Y = \left[ \lfloor p_{y} \rfloor, \lceil p_{y} \rceil \right] 
%\end{equation}
%
% \begin{equation}
% Z = \left[ \lfloor p_{z} \rfloor, \lceil p_{z} \rceil \right] 
%\end{equation}

\begin{equation}
	\vec{P} =
	\begin{bmatrix}
		X \\
 		Y \\
  		Z \\
	\end{bmatrix}
	=
	\begin{bmatrix}
		\; \lfloor \vec{p}_{\mathrm{POI}}(1) \rfloor \; \lceil \vec{p}_{\mathrm{POI}}(1) \rceil \;  \\
		\; \lfloor \vec{p}_{\mathrm{POI}}(2) \rfloor \; \lceil \vec{p}_{\mathrm{POI}}(2) \rceil \; \\
		\; \lfloor \vec{p}_{\mathrm{POI}}(3) \rfloor \; \lceil \vec{p}_{\mathrm{POI}}(3) \rceil \; 
	\end{bmatrix}
\end{equation}

\begin{equation}
	\vec{V}rep_{xyz} = \mathrm{calc\_rep\_vel}(X[i], Y[j], Z[k]) \quad \forall i, j, k \in \{1, 2\}
\end{equation}

%\begin{equation}
%	\Delta X = \frac{\left( P_x - X(1) \right)}{\left( X(2) - X(1) \right)}
%\end{equation}
%
%\begin{equation}
%	\Delta Y = \frac{\left( P_y - Y(1) \right)}{\left( Y(2) - Y(1) \right)}
%\end{equation}
%
%\begin{equation}
%	\Delta Z = \frac{\left( P_z - Z(1) \right)}{\left( Z(2) - Z(1) \right)}
%\end{equation}

\begin{equation}
	\Delta \vec{P} =
	\begin{bmatrix}
		\Delta x \\
		\Delta y \\
		\Delta z		
	\end{bmatrix}
	=
	\begin{bmatrix}
		 \frac{\left( P_x - X(1) \right)}{\left( X(2) - X(1) \right)} \\
		 \frac{\left( P_y - Y(1) \right)}{\left( Y(2) - Y(1) \right)} \\
		 \frac{\left( P_z - Z(1) \right)}{\left( Z(2) - Z(1) \right)} \\
 	\end{bmatrix}
\end{equation}

%\begin{equation}
%	\vec{V}_{rep,00} = \vec{V}_{rep,000}(1 - x_d) + \vec{V}_{rep,100}x_d
%\end{equation}
%\begin{equation}
%	\vec{V}_{rep,01} = \vec{V}_{rep,001}(1 - x_d) + \vec{V}_{rep,101}x_d
%\end{equation}
%\begin{equation}
%	\vec{V}_{rep,10} = \vec{V}_{rep,010}(1 - x_d) + \vec{V}_{rep,110}x_d
%\end{equation}
%\begin{equation}
%	\vec{V}_{rep,11} = \vec{V}_{rep,011}(1 - x_d) + \vec{V}_{rep,111}x_d
%\end{equation}

\begin{equation}
	\vec{V}rep_{xyz,jk} = \vec{V}rep_{xyz,0jk}(1 - \Delta x) + \vec{V}rep_{xyz,1jk} \, \Delta x \quad \forall \, j, k \in \{1, 2\}
\end{equation}

%\begin{equation}
%	\vec{V}rep_{xyz,0} = \vec{V}rep_{xyz,00}(1 - \Delta y) + \vec{V}rep_{xyz,10} \, \Delta y
%\end{equation}
%
%\begin{equation}
%	\vec{V}rep_{xyz,1} = \vec{V}rep_{xyz,01}(1 - \Delta y) + \vec{V}rep_{xyz,11} \, \Delta y
%\end{equation}

\begin{equation}
	\vec{V}rep_{xyz,k} = \vec{V}rep_{xyz,0k}(1 - \Delta y) + \vec{V}rep_{xyz,1k} \, \Delta y \quad \forall \, k \in \{1, 2\}
\end{equation}

\begin{equation}
	\vec{V}rep_{xyz} = \vec{V}rep_{xyz,0}(1 - \Delta z) + \vec{V}rep_{xyz,1} \, \Delta z 
\end{equation}

\comment{}{PLOT: surrounding cells}

@@

Subsequently, we separately perform trilinear interpolation for each direction of the repulsive velocity vector.

It is important to consider that the calculated repulsive velocity values are located at the centers of the cells. Therefore, during interpolation, we shift the values of the cells coordinates by half the resolution of the obstacle grid for each direction. This results in a repulsive velocity vector that transitions smoothly between the discrete values calculated at distinct points in the obstacle grid.
